The Skew-Normal Approximation of the Binomial Distribution

### 2011-01-20 project/paper/method-of-moments.tex
Added an alt section heading without math mode.
Addressed required revisions by adding 2 paragraphs to Restrictions section.

\subsection{Solving for $\mu$, $\sigma$, $\lambda$}

@@

To obtain an estimate for $\lambda$, we must put a few restrictions on $n$ and
$p$.

@@

Figure \ref{fig:sn-restriction-least-n} shows the least sample size required to
estimate $\lambda$ as a function of $p$. As expected, it is quite large when
$p$ is small and rapidly goes to 0 as $p$ increases; for example, when $p =
0.01$, $n$ must be $\geq 98$, but at $p = 0.2$, $n$ need only be $\geq 3$, a
trivial requirement to meet.

@@

The second scenario is when $n$ is fixed and we wish to solve for $p$. In this
case, we return to \eqref{eq:solving-the-restriction} for further factoring:

@@

>>>>

\subsection[Solving for mu, sigma, lambda]{Solving for $\mu$, $\sigma$, $\lambda$}

@@

Unfortunately, although better than the normal approximation, the skew-normal
is also not universally applicable. To obtain an estimate for $\lambda$, we
must put a few restrictions on $n$ and $p$.

@@

Figure \ref{fig:sn-restriction-least-n} shows the least sample size required to
estimate $\lambda$ as a function of $p$. As we would expect, it is larger when
$p$ is small and rapidly goes to 0 as $p$ increases; for example, when $p =
0.01$, $n$ must be $\geq 98$, but at $p = 0.2$, $n$ need only be $\geq 3$, a
trivial requirement to meet.

@@

The second scenario, primarily of academic interest, is when $n$ is fixed and
we wish to solve for $p$. In this case, we return to
\eqref{eq:solving-the-restriction} for further factoring:

@@

Although the presence of these restrictions are somewhat disappointing, we can
console ourselves with the observation that at the same $n$ and $p$, the
skew-normal yields substantially more accurate approximations than the normal
(see section \ref{subsec:mabs}). Thus while imperfect, it is nevertheless an
improvement.

Finally, one last consideration that bears mentioning is that the skew-normal
approximation will sometimes provide us with parameters that violate our
intuition. In particular, for small $p$ and $n$, equation \eqref{eq:mu-solved}
can yield negative values of $\mu$, which is impossible for the binomial. This
can be explained by the fact that as $n$ and $p$ grow more extreme, so does the
inaccuracy of our approximation. Rather than impose a hard restriction on these
cases, we would simply advise that the reader be aware of the limits of the
skew-normal and, if more accuracy is necessary, seek another method of
approximation.

### 2011-01-20 project/paper/output.tex
Added an alt section heading without math mode.
Addressed required revisions by adding 2 paragraphs to Restrictions section.

\section{Demonstrating Improved Accuracy}

@@

\subsection{Maximal Absolute Error}

>>>>

Although the presence of these restrictions are somewhat disappointing, we can
console ourselves with the observation that at the same $n$ and $p$, the
skew-normal yields substantially more accurate approximations than the normal
(see section \ref{subsec:mabs}). Thus while imperfect, it is nevertheless an
improvement.

Finally, one last consideration that bears mentioning is that the skew-normal
approximation will sometimes provide us with parameters that violate our
intuition. In particular, for small $p$ and $n$, equation \eqref{eq:mu-solved}
can yield negative values of $\mu$, which is impossible for the binomial. This
can be explained by the fact that as $n$ and $p$ grow more extreme, so does the
inaccuracy of our approximation. Rather than impose a hard restriction on these
cases, we would simply advise that the reader be aware of the limits of the
skew-normal and, if more accuracy is necessary, seek another method of
approximation.

\section{Demonstrating Improved Accuracy}
\label{sec:demonstrating-improved-accuracy}

@@

\subsection{Maximal Absolute Error}
\label{subsec:mabs}
